Supplement to: Inferring Graphics Programs from Images

### 2017-05-18 supplement.tex
better figure for multidimensional scaling result
including programs and parses in the supplement. it looks like I made some changes that made the synthesizer worse because it seems to be missing some programs I expected it to learn

>>>>

\section{Full results on drawings data set}

Below we show our full data set of drawings. The leftmost column is a hand drawing. The middle column is a rendering of the most likely trace discovered by the neurally guided SMC sampling scheme. The rightmost column is the program we synthesized from a ground truth execution trace of the drawing.
\input{synthesizerOutputs.tex}

### 2017-05-18 synthesizerOutputs.tex
including programs and parses in the supplement. it looks like I made some changes that made the synthesizer worse because it seems to be missing some programs I expected it to learn

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-94-parses/0.png}&

>>>>

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-1.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-1-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-5-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-16-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-18.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-18-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-20.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-20-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-34.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-34-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-36-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-38.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-38-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-39.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-39-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-50-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-56.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-56-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-60-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-71.png}&
            Sampled no finished traces.&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-73.png}&
            Sampled no finished traces.&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-77.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-77-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-79.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-79-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-80.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-80-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-82.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-82-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-83.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-83-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-84.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-84-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-86.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-86-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-89.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-89-parses/0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
Solver timeout
        \end{verbatim}
\end{minipage}

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
            Sampled no finished traces.&
